---
title: "Storyboard"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    
---
```{r include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
library(ggplot2)
library(shiny)
library(plotly)
dat<- read.csv("C:/Users/User/Desktop/STQD_ data visual/individual project/Sleep_health_and_lifestyle_dataset.csv", sep=",", header=TRUE)
```

Page {.storyboard}
=====================================

### Introduction
In the modern society, occupation plays an important role in the continuity of economic expansion, societal development, and environmental management. 

However, as important as the growth of modern society, sleep quality is often neglected and this might effect a person's lifestyle and health in the long run. 

Therefore, this project aims to study the sleep health and lifestyle of each occupation.




### 1:Occupation distribution

```{r}
ggplot(dat, aes(x="", fill=factor(Occupation)))+
  geom_bar(width=1)+coord_polar(theta="y")


```

***

This chart displays the 

distribution of occupation in the dataset.

It can be observed that the majority

of the dataset consist of nurses, and

doctors. 




### 2:duration of sleep vs sleep quality


```{r, fig.height=4, fig.width=4}
ggplotly(ggplot(dat, aes(x=Sleep.Duration, y=Quality.of.Sleep, group=Occupation, fill=Occupation))+
  geom_point(shape=21, aes(size=Quality.of.Sleep))+
  labs(colours="Occupation")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)))

```

***

we can see that the longer the sleep duration, the better the 

sleep quality. We can further see that the occupation with 

sleep quality value > 8 are teacher, engineer, lawyer & manager


### 3:sleep quality vs activity level


```{r}

ggplotly(ggplot(dat, aes(x = Quality.of.Sleep, y =Physical.Activity.Level,colour=Occupation, group = Occupation)) +
  geom_point() +
  labs(x ="sleep quality", y = "activity level", colours="Occupation") +
  theme_minimal())
```

***

from the plot, overall we see that sleep quality improves 

activity level. this is because as sleep quality increase, 

the activity level increase as well


### 4:stress level for each occupation


```{r}
ggplot(dat, aes(x = Occupation, y = Stress.Level, fill = Occupation)) +
  geom_bar(stat = "identity") +
  labs(x = "Occupation", y = "Stress Level") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

***

 next, we would like to observe the stress level for each 
 occupation. 
 
 This is to further understand the relationship 
 of stress level for each occupation. 
 
 As we can see, the occupation with highest stress level is doctor, 
 followed by nurse. In contrast, the lowest stress level belongs to managers


### 5: stress level and heart rate 



```{r}
ggplotly(ggplot(dat, aes(fill = Occupation, x = Stress.Level, y = Heart.Rate)) +
  geom_point() +
  labs(fill = "Occupation", x = "stress level", y = "Heart Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)))

```

***

 from here, we can see that as stress level increase, the heart 
 rate increases.However there are some outliers for lower stress 
 level where the heart rate is high. 
 
 There might be lifestyle or workstyle that would lead to high heart rate, which include 
 low physical activity level will also affect heart rate.
 
 
### 6: daily steps vs heart rate


```{r}
ggplotly(ggplot(dat, aes(fill = Occupation, x = Daily.Steps, y= Heart.Rate)) +
  geom_point() +
  labs(y = "heart rate", x = "Daily Steps") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)))

```

***

In conjunction to the previous plot, we can see that the 
daily steps have negative relationship towards heart rate. 

This is because we can observe that as daily step increase, 
the heart rate decreases. 

We can also see that doctor has the lowest heart rate as 
they have highest daily steps.

### 7: BMI category distribution


```{r}
ggplot(dat, aes(x = BMI.Category, fill = BMI.Category)) +
  geom_bar() +
  labs(x = "BMI Category", y = "Frequency", fill = "BMI Category") +
  theme_minimal()

```

***

next, we will evaluate the BMI relationship with other 
variables for each occupation.

this is because we wish to understand the relationship 
of BMI affecting or affected by the occupation, stress 
level, blood pressure and others. 

But first, we will see the general distribution of BMI 
category, and we observe that majority of the dataset 
participant belongs to normal, and followed by overweight.

### 8: BMI category vs blood pressure


```{r}
ggplotly(ggplot(dat, aes(fill = Occupation, y = Blood.Pressure, x= BMI.Category)) +
           geom_point() +
           labs(y = "blood pressure", x = "BMI category") +
           theme_minimal() +
           theme(axis.text.x = element_text(angle = 45, hjust = 1)))
```

***

from the plot, we can see the distribution of each occupation 
on the BMI and blood pressure.

this is to see that occupation that belongs to obese and
overweight will usually have high blood pressure.

this can come hand in hand with the stress level from the
previous plots.

as we can see, on average, the doctor has highest blood pressure 
and stress level (from previous plot). 

This can further infer that doctors have unhealthy lifestyle 
which results them to being obese generally.


### 9:  BMI vs sleep duration


```{r}
ggplotly(ggplot(dat, aes(fill = Occupation, y = Sleep.Duration, x= BMI.Category)) +
           geom_point() +
           labs(y = " sleep duration", x = "BMI Category") +
           theme_minimal() +
           theme(axis.text.x = element_text(angle = 45, hjust = 1)))
```

***

We can observe that for normal and normal weight, 
the sleep duration is mostly around 7 hours and above.

Whereas, for overweight, the sleep duration is mostly below 7 hour.

Therefore, we can assume that sleep duration has a 
positive relationship with BMI.

Lesser sleep will negatively affect BMI, and more 
sleep will result to better BMI.

### 10: sleep disorder vs BMI 


```{r}
ggplot(dat, aes(x = Sleep.Disorder, fill = BMI.Category)) +
  geom_bar() +
  labs(x = "Sleep Disorder", y = "Count", fill = "BMI Category") +
  theme_minimal()
```

***

Lastly, we wish to understand relationship between
sleep disorder affecting BMI category.

We see that when there is no sleep disorder, 
the BMI mostly will be normal and there is an equal 
distribution when there is a presence of sleep disorder, 
which leads to overweight.

Therefore, we can conclude that sleeping quality, 
including sleeping duration and absence of sleep disorder
will have a positive impact on BMI.

### Conclusion
In conclusion, we can infer that the doctor occupation are most stressful occupation as there is a high reading on stress level and blood pressure but have good sleep quality.

Then we move into a more in-depth study of how sleep and stress affects BMI, and we found that high blood pressure, poor sleep duration and presence of sleep disorder leads to poor BMI category.

Thus, we can conclude that any occupation have a mixed distribution of BMI reading. But the doctors and nurses have better lifestyle as they have better sleep quality and better health heart rate.

